### 2024-07-11 acronyms/acronyms.tex
nas
ept
nwf
cdo
ne585

\newacronym{nas}{NAS}{National Academies}

@@

>>>>

\newacronym{nas}{NAS}{National Academy of Sciences}

@@

\newacronym{ept}{EPAct}{Energy Policy Act}
\newacronym{nau}{NARUC}{National Association of Regulatory Utility Commissioners}
\newacronym{cdo}{CD-0}{Critical Decision-0}
\newacronym{mcp}{MCNP}{Monte Carlo N-Particle Transport Code}
\newacronym{ke}{KE}{Kinetic Energy}
\newacronym{swu}{SWU}{Separative Work Unit}
\newacronym{cp1}{CP-1}{Chicago Pile-1}
\newacronym{eb1}{EBR-I}{Experimental Breeder Reactor I}
\newacronym{eb2}{EBR-II}{Experimental Breeder Reactor II}
\newacronym{trt}{TREAT}{Transient Reactor Test Facility}
\newacronym{cdu}{CANDU}{Canada Deuterium Uranium Reactor}
\newacronym{sfr}{SFR}{Sodium Fast Reactor}
\newacronym{pur}{PUREX}{Plutonium Uranium Reduction Extraction}
\newacronym{mox}{MOX}{Mixed Oxide}
\newacronym{tbp}{TBP}{Tributyl Phosphate}
\newacronym{fp}{FP}{Fission Product}
\newacronym{lft}{LFTR}{Liquid Fluoride Thorium Reactor}
\newacronym{atr}{ATR}{Advanced Test Reactor}
\newacronym{rtg}{RTG}{Radioisotope Thermoelectric Generator}
\newacronym{vov}{VOV}{Variance of Variance}
\newacronym{wwg}{WWG}{Weight Window Generator}
\newacronym{ges}{GESMO}{Generic Environmental Impact Statement for Mixed Oxide Fuel}
\newacronym{omb}{OMB}{Office of Management and Budget}
\newacronym{tpa}{TSPA}{Total System Performance Assessment}
\newacronym{llw}{LLW}{Low Level Waste}
\newacronym{dnd}{D\&D}{Decontamination \& Decommissioning}
\newacronym{ebs}{EBS}{Engineered Barrier System}
\newacronym{ala}{ALARA}{As Low As Reasonably Achievable}
